A fast algorithm for global code motion of congruent instructions

### 2017-11-13 cgo/paper.tex
table caption

\begin{table}[h!]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|r|r|r|}
      \hline
Benchmarks        &base(-Ofast) &\GCM{}(-Ofast) &GCM/base\\\hline
400.perlbench	  & 2539	& 2493	& 0.98 \\\hline
401.bzip2	  & 718	        & 707	& 0.98 \\\hline
403.gcc	          & 5782	& 5722	& 0.99 \\\hline
429.mcf	          & 14	        & 17	& 1.21 \\\hline
433.milc	  & 635	        & 642	& 1.01 \\\hline
444.namd	  & 3223	& 3274	& 1.01 \\\hline
445.gobmk	  & 2166	& 2173	& 1.00 \\\hline
447.dealII	  & 11074	& 10234	& 0.92 \\\hline
450.soplex	  & 1122	& 1125	& 1.00 \\\hline
453.povray	  & 4701	& 4692	& 1.09 \\\hline
456.hmmer	  & 1197	& 1274	& 1.06 \\\hline
458.sjeng	  & 168	        & 176	& 1.05 \\\hline
462.libquantum	  & 118	        & 118	& 1.00 \\\hline
464.h264ref	  & 3379	& 3454	& 1.02 \\\hline
470.lbm	          & 33	        & 33	& 1.00 \\\hline
471.omnetpp	  & 524	        & 527	& 1.00 \\\hline
473.astar	  & 180	        & 201	& 1.12 \\\hline
482.sphinx3	  & 674	        & 670	& 0.99 \\\hline
483.xalancbmk	  & 5102	& 4965	& 0.97 \\\hline
Grand Total	  & 43349	& 42497	& 0.98 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Number of spills before and after \gcm{}(\GCM{}) on SPEC2006 at
    -Ofast. Lower is better in \%age change. Spills reduced by 2\%.}
  \label{tab:spills}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|c|c|c|}
      \hline
      Benchmarks      &   Baseline	        & \GCM{}           & \%Decrease\\
       & (in Millions)& (in Millions)& (lower is better)\\\hline
  400.perlbench	  &   186	& 184	& 0.99 \\\hline
  401.bzip2	  &   76	& 75	& 0.99 \\\hline
  403.gcc         &   1,079	& 1,073	& 0.99 \\\hline
  429.mcf         &   78	& 77	& 0.99 \\\hline
  433.milc	  &   272	& 269	& 0.99 \\\hline
  444.namd	  &   78	& 77	& 0.99 \\\hline
  445.gobmk	  &   261	& 258	& 0.99 \\\hline
  447.dealII	  &   643	& 638	& 0.99 \\\hline
  450.soplex	  &   245	& 242	& 0.99 \\\hline
  453.povray	  &   499	& 494	& 0.99 \\\hline
  456.hmmer	  &   214	& 211	& 0.99 \\\hline
  458.sjeng	  &   89	& 88	& 0.99 \\\hline
  462.libquantum  &   84	& 84	& 0.99 \\\hline
  464.h264ref	  &   151	& 149	& 0.99 \\\hline
  470.lbm         &   71	& 71	& 1.00 \\\hline
  471.omnetpp	  &   382	& 379	& 0.99 \\\hline
  473.astar	  &   78	& 77	& 0.99 \\\hline
  482.sphinx3	  &   158	& 156	& 0.99 \\\hline
  483.xalancbmk	  &   22,485	& 22,455& 1.00 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Change in total number of instructions executed during the
    compilation with and without \gcm{} (\GCM{}) on \SPEC{} at -Ofast. The
    instructions were counted using valgrind.}
  \label{tab:compile-time}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.8}{
    \begin{tabular}{|l|r|r|r|r|}
      \hline
      &\multicolumn{2}{|c|}{Loop Invariant Motion}  & \multicolumn{2}{|c|}{Functions} \\\hline
 Benchmarks       & Hoisted \% & Sunk \% &  Inlined\%   & Deleted\% \\\hline
 400.perlbench	  & 2.1 & -2.8 &  0.2 &  0.9  \\\hline
 401.bzip2	  & 14.4& 0.0  &  4.7 &  3.1  \\\hline
 403.gcc	  & 13.7& 27.3 &  0.9 &  0.1  \\\hline
 429.mcf	  & -7.3& 0.0  &  0.0 &  0.0  \\\hline
 433.milc	  & 10.2& 0.0  &  8.0 &  0.0  \\\hline
 444.namd	  & 0.1 & 0.0  &  0.8 &  -3.5 \\\hline
 445.gobmk	  & 0.6 & 5.6  &  5.4 &  1.7  \\\hline
 447.dealII	  & 62.2& -86.7& -0.2 &  -0.8 \\\hline
 450.soplex	  & 3.9 & -5.6 & -0.2 &  -0.4 \\\hline
 453.povray	  & -4.8& 39.1 &  0.2 &  -0.1 \\\hline
 456.hmmer	  & 1.0 & 166.7&  0.0 &  -1.9 \\\hline
 458.sjeng	  & 11.5& 0.0  &  6.3 &  0.0  \\\hline
 462.libquantum   & 6.6 & 0.0  &  0.0 &  0.0  \\\hline
 464.h264ref	  & 0.5 & 0.0  &  13.0&  0.0  \\\hline
 470.lbm	  & 0.0 & 0.0  &  0.0 &  0.0  \\\hline
 471.omnetpp	  & 17.0& -6.3 &  1.1 &  -0.4 \\\hline
 473.astar	  & 9.1 & 0.0  &  1.1 &  0.0  \\\hline
 482.sphinx3	  & 5.9 & -18.2&  -2.0&  0.0  \\\hline
 483.xalancbmk	  & 14.6& -3.6 &  -1.0&  -1.2 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Change in the static compile time metrics w.r.t. \gcm{} (\GCM{}) on
    \SPEC{} at -Ofast. The \% columns show percentage increase in metric
    w.r.t. baseline. \GCM{} improves LICM and inlining in general.}
  \label{tab:stats}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|r|r|r|}
      \hline
Benchmarks        &base(-Ofast) &\GCM{}(-Ofast) &GCM/base\\\hline
400.perlbench	  & 2539	& 2493	& 0.98 \\\hline
401.bzip2	  & 718	        & 707	& 0.98 \\\hline
403.gcc	          & 5782	& 5722	& 0.99 \\\hline
429.mcf	          & 14	        & 17	& 1.21 \\\hline
433.milc	  & 635	        & 642	& 1.01 \\\hline
444.namd	  & 3223	& 3274	& 1.01 \\\hline
445.gobmk	  & 2166	& 2173	& 1.00 \\\hline
447.dealII	  & 11074	& 10234	& 0.92 \\\hline
450.soplex	  & 1122	& 1125	& 1.00 \\\hline
453.povray	  & 4701	& 4692	& 1.09 \\\hline
456.hmmer	  & 1197	& 1274	& 1.06 \\\hline
458.sjeng	  & 168	        & 176	& 1.05 \\\hline
462.libquantum	  & 118	        & 118	& 1.00 \\\hline
464.h264ref	  & 3379	& 3454	& 1.02 \\\hline
470.lbm	          & 33	        & 33	& 1.00 \\\hline
471.omnetpp	  & 524	        & 527	& 1.00 \\\hline
473.astar	  & 180	        & 201	& 1.12 \\\hline
482.sphinx3	  & 674	        & 670	& 0.99 \\\hline
483.xalancbmk	  & 5102	& 4965	& 0.97 \\\hline
Grand Total	  & 43349	& 42497	& 0.98 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Number of spills with and without\GCM{} on SPEC2006 at
    -Ofast. Lower is better in GCM/base. Spills reduced by 2\%.}
  \label{tab:spills}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|c|c|c|}
      \hline
      Benchmarks      &   Baseline	        & \GCM{}           & \%Decrease\\
       & (in Millions)& (in Millions)& (lower is better)\\\hline
  400.perlbench	  &   186	& 184	& 0.99 \\\hline
  401.bzip2	  &   76	& 75	& 0.99 \\\hline
  403.gcc         &   1,079	& 1,073	& 0.99 \\\hline
  429.mcf         &   78	& 77	& 0.99 \\\hline
  433.milc	  &   272	& 269	& 0.99 \\\hline
  444.namd	  &   78	& 77	& 0.99 \\\hline
  445.gobmk	  &   261	& 258	& 0.99 \\\hline
  447.dealII	  &   643	& 638	& 0.99 \\\hline
  450.soplex	  &   245	& 242	& 0.99 \\\hline
  453.povray	  &   499	& 494	& 0.99 \\\hline
  456.hmmer	  &   214	& 211	& 0.99 \\\hline
  458.sjeng	  &   89	& 88	& 0.99 \\\hline
  462.libquantum  &   84	& 84	& 0.99 \\\hline
  464.h264ref	  &   151	& 149	& 0.99 \\\hline
  470.lbm         &   71	& 71	& 1.00 \\\hline
  471.omnetpp	  &   382	& 379	& 0.99 \\\hline
  473.astar	  &   78	& 77	& 0.99 \\\hline
  482.sphinx3	  &   158	& 156	& 0.99 \\\hline
  483.xalancbmk	  &   22,485	& 22,455& 1.00 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Change in total number of instructions executed during the
    compilation with and without \GCM{} on \SPEC{} at -Ofast. The
    instructions were counted using valgrind.}
  \label{tab:compile-time}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.8}{
    \begin{tabular}{|l|r|r|r|r|}
      \hline
      &\multicolumn{2}{|c|}{Loop Invariant Motion}  & \multicolumn{2}{|c|}{Functions} \\\hline
 Benchmarks       & Hoisted \% & Sunk \% &  Inlined\%   & Deleted\% \\\hline
 400.perlbench	  & 2.1 & -2.8 &  0.2 &  0.9  \\\hline
 401.bzip2	  & 14.4& 0.0  &  4.7 &  3.1  \\\hline
 403.gcc	  & 13.7& 27.3 &  0.9 &  0.1  \\\hline
 429.mcf	  & -7.3& 0.0  &  0.0 &  0.0  \\\hline
 433.milc	  & 10.2& 0.0  &  8.0 &  0.0  \\\hline
 444.namd	  & 0.1 & 0.0  &  0.8 &  -3.5 \\\hline
 445.gobmk	  & 0.6 & 5.6  &  5.4 &  1.7  \\\hline
 447.dealII	  & 62.2& -86.7& -0.2 &  -0.8 \\\hline
 450.soplex	  & 3.9 & -5.6 & -0.2 &  -0.4 \\\hline
 453.povray	  & -4.8& 39.1 &  0.2 &  -0.1 \\\hline
 456.hmmer	  & 1.0 & 166.7&  0.0 &  -1.9 \\\hline
 458.sjeng	  & 11.5& 0.0  &  6.3 &  0.0  \\\hline
 462.libquantum   & 6.6 & 0.0  &  0.0 &  0.0  \\\hline
 464.h264ref	  & 0.5 & 0.0  &  13.0&  0.0  \\\hline
 470.lbm	  & 0.0 & 0.0  &  0.0 &  0.0  \\\hline
 471.omnetpp	  & 17.0& -6.3 &  1.1 &  -0.4 \\\hline
 473.astar	  & 9.1 & 0.0  &  1.1 &  0.0  \\\hline
 482.sphinx3	  & 5.9 & -18.2&  -2.0&  0.0  \\\hline
 483.xalancbmk	  & 14.6& -3.6 &  -1.0&  -1.2 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Change in the static compile time metrics w.r.t. \GCM{} on
    \SPEC{} at -Ofast. The \% columns show percentage increase in metric
    w.r.t. baseline. \GCM{} improves LICM and inlining in general.}
  \label{tab:stats}
\end{table}
